\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-13 ms.tex
Update on Overleaf.
improve fig

% TODO: after submission
% - Split cluster into 2? Price-Whelan 1a and 1b?
% - discuss Blanco 1: high latitude, similar age, high binary fraction
% - Make a PGM for this model?

@@

\author[0000-0003-2808-275X]{Douglas~P.~Finkbeiner}
\affiliation{Institute for Theory and Computation, Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}

@@

We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association in the Milky Way halo: \clustername.
At a Galactocentric cylindrical position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $D \approx \cldist$.
At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with Milky Way disk.
The estimated age of \clustername\ is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by the last disk midplane passage, which occurred at a Galactocentric radius $R \approx 30~\kpc$.
However, most details of this idea remain a mystery: the Magellanic stream has low column density, the Milky Way disk at this large radius has low gas density, and the relative velocity of the leading arm gas and Milky Way gas is large. However it formed, the discovery of a young stellar cluster in the Milky Way halo presents an interesting opportunity for study.
\end{abstract}

@@

The Magellanic stream (MS), including gas in the leading arm (LA), is a large stream of predominantly hydrogen gas emanating from the \lmcsmc\ system that contains a significant fraction of the total gas mass associated with the \lmcsmc\ \citep{Bruns:2005} and wraps nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
The trailing MS has been studied in great detail by large-area and high-resolution radio sky surveys: Recent surveys have found small-scale structure and gas fragmentation \citep[e.g.,][]{Nidever:2008, For:2014} and a large-scale bifurcation, with kinematically \citep{Nidever:2008} and chemically \citep{Fox:2013} distinct ``strands'' that lead back to the LMC and the SMC.
The LA gas has been found to connect to regions of low-column-density gas ($N\sim 10^{18}$--$10^{19}~\textrm{cm}^{-2}$) on the other side of the Galactic disk \citep{Putman:1998, Nidever:2008}, and has been decomposed into distinct gas features named LA1--4 \citep{Bruns:2005, Nidever:2008, Venzmer:2012}.
%that contain a small fraction of the total MS mass \citep[$\sim 4 \times10^7~\msun$;][]{Venzmer:2012}.

The origin and formation of the LA features of the MS is still uncertain.
Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC \citep{Putman:1998}, but it has also been argued that outer features of the LMC appear to lead directly into the LA1 feature, implying an LMC origin \citep{Nidever:2008}.
Recent chemical abundance measurements along several sight-lines passing through the LA again suggested the SMC origin \citep{Fox:2018, Richter:2018}.
Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the LA \citep{Nidever:2008, Besla:2012}.
However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions with gas in the outer Milky Way disk (from the recent disk plane passage) may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.

@@

In this \articlename, we report the discovery of a young stellar cluster at the far edge of the LA-2 feature ($L_{\textrm{MS}} \sim 65^\circ$) that is located far into the Galactic halo ($D \sim \cldist$) and therefore plausibly formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
This provides the first precise distance measurement to the MS leading arm to be compared with simulations of the \lmcsmc\ in the Milky Way, and provides an opportunity to study recent star formation in a unique environment.
The discovery of \clustername\ will enable new modeling efforts that track the infall of the \lmcsmc, the tidal stripping of Magellanic gas, and the interaction of this gas with the Milky Way.

In \sectionname~\ref{sec:data}, we present the initial discovery with \gaia\ \DR{2} and follow-up observations with \decam\ to obtain deeper photometry of the region around the association.
In \sectionname~\ref{sec:results}, we use the \gaia\ data to measure the kinematics, and \decam\ photometry to infer the age, metallicity, and distance to \clustername, and discuss plausible formation scenarios.
% In \sectionname~\ref{sec:discussion}, we discuss implications for future searches for stars associated with the MS, and discrepancies with existing models of the LA.
We conclude in \sectionname~\ref{sec:conclusion}.

@@

We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) to search for distant, comoving multiplets of blue stars.
Our original intent was to search for small, distant, comoving groups of blue horizontal branch stars to identify new candidate satellites of the Milky Way.
We therefore initially select all stars from \gaia\ with parallax $\varpi < 1$, color $-0.5 < (\bprp) < 0$, $G$-band magnitude $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see Appendix~\ref{sec:queries} for database query).
We further exclude stars within a $15^\circ$ radius from the LMC, and a $8^\circ$ radius from the SMC --- 27,895 stars remain after these cuts.
We then cross-match this catalog to itself with both sky positions and proper motions: we search for pairs of stars that have separations $s < 0.5^\circ$ and proper motion differences $|\Delta \mu| < 0.5~\masyr$.
We then combine mutually-connected comoving pairs into small groups of stars that are colocated on the sky and comoving in proper motions, and remove groups that have $<4$ members.
We cross-match the mean sky positions of the groups to locations of local group galaxies \citep{McConnachie:2012} and Milky Way globular clusters \citep[2010 edition;][]{Harris:1996} and filter out all groups that lie within 1 degree of these known objects.
After these filters, just one group of blue, comoving stars remains at $(\textrm{RA}, \textrm{Dec}) \sim (179, -29)^\circ$.

@@

We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on a portion of the cluster discovered using the \gaia\ data (see previous section).  Observations were obtained with the Dark Energy Camera (DECam) on the CTIO 4m Blanco telescope on UT 2018 May 20 with 3$\times$300s
exposures in $u-$, $g-$, and $i$-band.  The NOAO Community Pipeline (CP; \citealt{Valdes:2014}; Valdes et al., in preparation) InstCal images, which have the instrumental signature removed, were downloaded from the NOAO Archive\footnote{\url{http://archive.noao.edu}} for further processing.  Forced PSF photometry was performed with the PHOTRED pipeline \citep{Nidever:2017} which uses the DAOPHOT ALLSTAR \citep{Stetson:1987} and ALLFRAME \citep{Stetson:1994} suite of programs.  The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for
global zero-point and color-terms in each band.
%\todo{Nidever: can you describe the observations? Exposure times, dither, whatever is usually done...}
%The photometry was reduced...\todo{Nidever: describe your pipeline?}

@@

In the subsections below, we perform two independent analyses of the data available for \clustername.
First, in \sectionname~\ref{sec:pmclean}, we use astrometric data from \gaia\ \DR{2} to determine the mean proper motion of the cluster by modeling the kinematics of the cluster and background sources.
Then, in \sectionname~\ref{sec:popmodel}, we use photometric data from \decam\ to assign membership probabilities to sources and simultaneously infer the cluster stellar population parameters (age, metallicity, distance, etc.).
We perform these analyses separately because \gaia\ \DR{2} only includes the most massive members of the cluster, but the addition of lower main sequence members apparent in the \decam\ photometry provide a much better constraint on the cluster parameters.

@@

\subsection{Inferring the mean proper motion}
\label{sec:pmclean}

We measure the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background populations using astrometric data from \gaia.
We start by selecting all stars with $(\bprp)_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
\figurename~\ref{fig:pm-members}, left (grey points), shows the sky positions of stars that pass this blue cut in the region around the young cluster.
The larger solid-line circle indicates the region we define as the cluster area, and the two smaller dashed-line circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
The control fields are designed to, together, have the same total area as the cluster field, and were chosen to have similar latitudes as the cluster field in the Magellanic stream coordinate system \citep{Nidever:2008}.
The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.
The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$ is the identified comoving association of blue stars.\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.}
Note that \figurename~\ref{fig:pm-members} is only meant an illustration: The cluster proper motion is determined probabilistically by taking into account the full \gaia\ covariance matrices for each source, as described below.

@@

We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{emcee, Goodman:2010} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
For the young cluster, we find $\bs{x} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
The proper-motion dispersion is consistent with zero, and is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.
\tablename~\ref{tbl:gaiadata} contains a subset of the \gaia\ \DR{2} data for stars in the cluster field, with kinematic membership probabilities determined from this modeling procedure.

\subsection{Inferring the stellar population parameters}
\label{sec:popmodel}

@@

\begin{table}[htb]
\begin{center}
    \begin{tabular}{ c | c | c }
        \toprule
        Parameter & Prior & Bounds \\
        \toprule
        $\tau$ & uniform & $(10~\textrm{Myr}, 15~\textrm{Gyr})$ \\
        $\feh$ & uniform & $(-2, 0.5)$ \\
        $\eep$ & (see caption) & $(202, 355)$ \\
        $A_V$ & $\propto A_V^{-1}$ & $(0.001, 1)~\textrm{mag}$ \\
        $D$ & $\propto D^{2}$ & $(1, 100)~\kpc$ \\
        \toprule
    \end{tabular}
\caption{Prior probability distributions for each of the stellar parameters defined in \sectionname~\ref{sec:popmodel}, used for the independent (per star) posterior samplings.
The prior on \eep\ is computed by calculating the stellar mass, $m$, corresponding to a given point in the isochrone parameter space, $(\eep, \tau, \feh)$, and computing the probability from a Salpeter \citep{Salpeter:1955} mass prior such that $p(\eep) = p(m)\,\left|\frac{\dd m}{\dd \eep}\right|$, following the prescription used in \texttt{isochrones} \citep{Morton:2015}.
\label{tbl:priors}}
\end{center}
\end{table}

@@

\begin{table}[hbt]
\begin{center}
    \begin{tabular}{ c | c | c }
        \toprule
        Parameter & Prior & Bounds \\
        \toprule
        $\tau^*$ & uniform & $(1~\textrm{Myr}, 1~\textrm{Gyr})$ \\
        $\feh^*$ & uniform & $(-2, 0)$ \\
        $A_V^*$ & uniform & $(0, 1)~\textrm{mag}$ \\
        $D^*$ & uniform & $(1, 100)~\kpc$ \\
        $f$ & uniform & (0, 1) \\
        \toprule
    \end{tabular}
\caption{Prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, used for the hierarchical inference of the cluster stellar population parameters.
\label{tbl:hyperpriors}}
\end{center}
\end{table}

@@

Ignoring the disk gas (between $V_{\textrm{LSR}} \sim -20$--$20~\kms$ in \figurename~\ref{fig:gasspv}), it seems that there are three qualitatively different line-of-sight velocities that the gas (and plausibly \clustername) could have: $V_{\textrm{LSR}} \approx (60, 110, 230)~\kms$.
If we adopt these velocity measurements as the line-of-sight (LOS) velocity of \clustername, we have measurements of all 6 phase-space components and can compute orbits for the cluster.
We compute Galactic orbits of the cluster using each of the three values of the line-of-sight velocity from the LA II region filaments.
\figurename~\ref{fig:orbits} shows these three orbits computed by integrating the position of \clustername\ backwards in time:
The two panels of \figurename~\ref{fig:orbits} show the Galactocentric Cartesian trajectories of \clustername\ over the last $260~\textrm{Myr}$ by assuming each of the three plausible line-of-sight velocities discussed above (as labeled in the right panel).
To compute the orbits, we use a three-component Milky Way mass model consisting of a disk \citep{Miyamoto:1975}, a bulge \citep{Hernquist:1990}, and a spherical dark matter halo \citep{Navarro:1996}.
The parameters of this model are set to match the circular velocity profile and disk properties of \citet{Bovy:2015}, and is implemented in the \texttt{gala} package \citep{gala} as the \texttt{MilkyWayPotential}.
We note that we do not include the LMC/SMC as a component of our mass model.

Also shown in \figurename~\ref{fig:orbits} is the present-day location of the LMC (open black circle), the present-day location of \clustername\ (filled black circle), the past orbit of the LMC over the same period, and the projected future orbit of the LMC (dashed line).
For the two lower LOS velocity cases, the orbit of \clustername\ crosses the midplane of the Galactic disk at a time comparable to the age of the cluster (i.e. when the color is darkest, corresponding to a time $\approx -130~\textrm{Myr}$).

However, note that while the orbits of \clustername\ and the LMC are generally in the same orbital plane and have the same sense about the Galaxy, none of the orbits closely approach or cross the orbit of the LMC.
This is expected if the gas shocked or otherwise lost kinetic energy through, e.g., ram pressure --- as is expected to explain the morphology of the LA material \citep[e.g.,][]{Hammer:2015} --- during or before the star formation event that produced \clustername.

@@

>>>>

% TODO: after submission?
% - Split cluster into 2? Price-Whelan 1a and 1b?
% - discuss Blanco 1: high latitude, similar age, high binary fraction
% - Make a PGM for this model?

@@

% \author[0000-0003-2808-275X]{Douglas~P.~Finkbeiner}
% \affiliation{Institute for Theory and Computation, Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}

@@

We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association in the Milky Way halo: \clustername.
From isochrone fitting to deeper, follow-up \decam\ imaging of the cluster, we also measure its distance, $D \approx \cldist$.
At its present Galactocentric cylindrical position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
If we assume that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the leading arm of the Magellanic stream.
At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with Milky Way disk.
The estimated age of \clustername\ is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by the last disk midplane passage, which occurred at a Galactocentric radius $R \approx 30~\kpc$.
However, most details of this idea remain a mystery: the Magellanic stream has low column density, the Milky Way disk at this large radius has low gas density, and the relative velocity of the leading arm gas and Milky Way gas is large. However it formed, the discovery of a young stellar cluster in the Milky Way halo presents an interesting opportunity for study.
\end{abstract}

@@

The Magellanic stream (MS), including gas in the leading arm (LA), is a large stream of predominantly hydrogen gas emanating from the \lmcsmc\ system that contains a significant fraction of the total gas mass associated with the \lmcsmc\ \citep{Bruns:2005} and wraps nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
The trailing MS has been studied in great detail by large-area and high-resolution radio sky surveys: Recent surveys have found small-scale structure and gas fragmentation \citep[e.g.,][]{Nidever:2008, For:2014} and a large-scale bifurcation, with kinematically \citep{Nidever:2008} and chemically \citep{Fox:2013} distinct ``strands'' that lead back to the LMC and the SMC.
The LA gas has been found to connect to regions of low-column-density gas ($N\sim 10^{18}$--$10^{19}~\textrm{cm}^{-2}$) on the other side of the Galactic disk \citep{Putman:1998, Nidever:2008}, and has been decomposed into distinct gas features named LA I--IV \citep{Bruns:2005, Nidever:2008, Venzmer:2012}.
%that contain a small fraction of the total MS mass \citep[$\sim 4 \times10^7~\msun$;][]{Venzmer:2012}.

The origin and formation of the LA features of the MS is still uncertain.
Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC \citep{Putman:1998}, but it has also been argued that outer features of the LMC appear to lead directly into the LA I feature, implying an LMC origin \citep{Nidever:2008}.
Recent chemical abundance measurements along several sight-lines passing through the LA again suggested the SMC origin \citep{Fox:2018, Richter:2018}.
Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the LA \citep{Nidever:2008, Besla:2012}.
However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions with gas in the outer Milky Way disk (from the recent disk plane passage) may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.

@@

In this \articlename, we report the discovery of a young stellar cluster at the far edge of the LA II feature ($L_{\textrm{MS}} \sim 65^\circ$) that is located far into the Galactic halo ($D \sim \cldist$) and therefore plausibly formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
This provides the first precise distance measurement to the MS leading arm to be compared with simulations of the \lmcsmc\ in the Milky Way, and provides an opportunity to study recent star formation in a unique environment.
The discovery of \clustername\ will enable new modeling efforts that track the infall of the \lmcsmc, the tidal stripping of Magellanic gas, and the interaction of this gas with the Milky Way.

In \sectionname~\ref{sec:data}, we present the initial discovery with \gaia\ \DR{2} and follow-up observations with \decam\ to obtain deeper photometry of the region around the association.
In \sectionname~\ref{sec:methods}, we use the \gaia\ data to measure the kinematics, and \decam\ photometry to infer the age, metallicity, and distance to \clustername
In \sectionname~\ref{sec:results}, we interpret the inferred stellar population parameters of \clustername\ and discuss plausible formation scenarios.
% In \sectionname~\ref{sec:discussion}, we discuss implications for future searches for stars associated with the MS, and discrepancies with existing models of the LA.
We conclude in \sectionname~\ref{sec:conclusion}.

@@

We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) to search for distant, comoving multiplets of blue stars.
Our original intent was to search for small, distant, comoving groups of blue horizontal branch stars to identify new candidate satellites of the Milky Way.
We therefore initially select all stars from \gaia\ with parallax $\varpi < 1$, color $-0.5 < (\bprp) < 0$, $G$-band magnitude $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see Appendix~\ref{sec:queries} for the database query).
We further exclude stars within a $15^\circ$ radius from the LMC, and a $8^\circ$ radius from the SMC --- 27,895 stars remain after these cuts.
We then cross-match this catalog to itself with both sky positions and proper motions: we search for pairs of stars that have separations $s < 0.5^\circ$ and proper motion differences $|\Delta \mu| < 0.5~\masyr$.
We then combine mutually-connected comoving pairs into small groups of stars that are colocated on the sky and comoving in proper motions, and remove groups that have $<4$ members.
We cross-match the mean sky positions of the groups to locations of local group galaxies \citep{McConnachie:2012} and Milky Way globular clusters \citep[2010 edition;][]{Harris:1996} and filter out all groups that lie within 1 degree of these known objects.
After these filters, just one group of blue, comoving stars remains at $(\textrm{RA}, \textrm{Dec}) \sim (179, -29)^\circ$.

@@

We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on a portion of the cluster discovered using the \gaia\ data (see previous section).  Observations were obtained with the Dark Energy Camera (DECam) on the CTIO 4m Blanco telescope on UT 2018 May 20 with 3$\times$300s
exposures in $u-$, $g-$, and $i$-band.  The NOAO Community Pipeline (CP; \citealt{Valdes:2014}; Valdes et al., in preparation) InstCal images, which have the instrumental signature removed, were downloaded from the NOAO Archive\footnote{\url{http://archive.noao.edu}} for further processing.  Forced PSF photometry was performed with the PHOTRED pipeline \citep{Nidever:2017} which uses the DAOPHOT ALLSTAR \citep{Stetson:1987} and ALLFRAME \citep{Stetson:1994} suite of programs.  The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for
global zero-point and color-terms in each band.

@@

In the subsections below, we perform two independent analyses of the data available for \clustername.
First, in \sectionname~\ref{sec:pmclean}, we use astrometric data from \gaia\ \DR{2} to determine the mean proper motion of the cluster by modeling the kinematics of the cluster and background sources.
Then, in \sectionname~\ref{sec:popmodel}, we use photometric data from \decam\ to assign membership probabilities to sources and simultaneously infer the cluster stellar population parameters (age, metallicity, distance, etc.).
We perform these analyses separately because \gaia\ \DR{2} only includes the most massive members of the cluster, but the addition of lower main sequence members apparent in the \decam\ photometry provide a much better constraint on the cluster parameters.
The parameters derived from this analysis are summarized in \tablename~\ref{tbl:clusterparams}.

@@

\subsection{Inferring the mean proper motion with \gaia}
\label{sec:pmclean}

We measure the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background populations using astrometric data from \gaia.
We start by selecting all stars with $(\bprp)_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
\figurename~\ref{fig:pm-members}, left (grey points), shows the sky positions of stars that pass this blue cut in the region around the young cluster.
The larger solid-line circle indicates the region we define as the cluster area, and the two smaller dashed-line circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
The control fields are designed to, together, have the same total area as the cluster field, and were chosen to have similar latitudes as the cluster field in the Magellanic stream coordinate system \citep{Nidever:2008}.
The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.
The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$ is the identified comoving association of blue stars.\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.}
Note that \figurename~\ref{fig:pm-members} is only meant as an illustration: The cluster proper motion is determined probabilistically by taking into account the full \gaia\ covariance matrices for each source, as described below.

@@

We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{emcee, Goodman:2010} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
For the young cluster, we find $\bs{x} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
The proper-motion dispersion is consistent with zero, and is likely unmeasured, because of the proper motion uncertainties; 95\% of the posterior samples have $s < 0.09~\masyr$.
\tablename~\ref{tbl:gaiadata} contains a subset of the \gaia\ \DR{2} data for stars in the cluster field, with kinematic membership probabilities determined from this modeling procedure.

\subsection{Inferring the stellar population parameters with \decam photometry}
\label{sec:popmodel}

@@

\begin{table}[htb]
\begin{center}
    \begin{tabular}{ c | c | c }
        \toprule
        Parameter & Prior & Bounds \\
        \toprule
        $\tau$ & uniform & $(10~\textrm{Myr}, 15~\textrm{Gyr})$ \\
        $\feh$ & uniform & $(-2, 0.5)$ \\
        $\eep$ & (see caption) & $(202, 355)$ \\
        $A_V$ & $\propto A_V^{-1}$ & $(0.001, 1)~\textrm{mag}$ \\
        $D$ & $\propto D^{2}$ & $(1, 100)~\kpc$ \\
        \toprule
    \end{tabular}
\caption{Prior probability distributions for each of the stellar parameters defined in \sectionname~\ref{sec:popmodel}, used for the independent (per star) posterior samplings.
The stellar parameters here are the ``equal evolutionary point'' number $\eep$, age $\tau$, metallicity $\feh$, extinction $A_V$, and distance $D$.
The prior on \eep\ is computed by calculating the stellar mass, $m$, corresponding to a given point in the isochrone parameter space, $(\eep, \tau, \feh)$, and computing the probability from a Salpeter \citep{Salpeter:1955} mass prior such that $p(\eep) = p(m)\,\left|\frac{\dd m}{\dd \eep}\right|$, following the prescription used in \texttt{isochrones} \citep{Morton:2015}.
\label{tbl:priors}}
\end{center}
\end{table}

@@

\begin{table}[hbt]
\begin{center}
    \begin{tabular}{ c | c | c }
        \toprule
        Parameter & Prior & Bounds \\
        \toprule
        $\tau^*$ & uniform & $(1~\textrm{Myr}, 1~\textrm{Gyr})$ \\
        $\feh^*$ & uniform & $(-2, 0)$ \\
        $A_V^*$ & uniform & $(0, 1)~\textrm{mag}$ \\
        $D^*$ & uniform & $(1, 100)~\kpc$ \\
        $f$ & uniform & (0, 1) \\
        \toprule
    \end{tabular}
\caption{Prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, used for the hierarchical inference of the cluster stellar population parameters.
The cluster parameters here are the cluster age $\tau^*$, metallicity $\feh^*$, extinction $A_V^*$, and distance $D^*$, and the fraction of stars in the field that belong to the cluster $f$.
\label{tbl:hyperpriors}}
\end{center}
\end{table}

@@

Ignoring the disk gas (between $V_{\textrm{LSR}} \sim -20$--$20~\kms$ in \figurename~\ref{fig:gasspv}), it seems that there are three qualitatively different line-of-sight velocities that the gas (and plausibly \clustername) could have: $V_{\textrm{LSR}} \approx (60, 110, 230)~\kms$.
If we adopt these velocity measurements as the line-of-sight (LOS) velocity of \clustername, we have measurements of all 6 phase-space components and can compute orbits for the cluster.
We compute Galactic orbits of the cluster using each of the three values of the line-of-sight velocity from the LA II region filaments.
\figurename~\ref{fig:orbits} shows these three orbits computed by integrating the position of \clustername\ backwards in time:
The two panels of \figurename~\ref{fig:orbits} show the Galactocentric Cartesian trajectories of \clustername\ over the last $260~\textrm{Myr}$ by assuming each of the three plausible line-of-sight velocities discussed above (as labeled in the right panel).
To compute the orbits, we use a three-component Milky Way mass model consisting of a disk \citep{Miyamoto:1975}, a bulge \citep{Hernquist:1990}, and a spherical dark matter halo \citep{Navarro:1996}.
The parameters of this model are set to match the circular velocity profile and disk properties of \citet{Bovy:2015}, and is implemented in the \texttt{gala} package \citep{gala} as the \texttt{MilkyWayPotential}.

We tried including an LMC component as a Hernquist sphere \citep{Hernquist:1990} with masses between $10^{10}$--$2.5\times 10^{11}~\msun$, but find that the orbit of \clustername\ does not change much over the integration period.
If the LMC mass were as high as $8\times 10^{11}~\msun$, all three orbits of \clustername\ return to and end up bound to the LMC, but at this large of a mass, the assumption of a fixed Milky Way reference frame is invalid.
We therefore neglect \lmcsmc\ component in what follows, and present an alternate interpretation below.

Also shown in \figurename~\ref{fig:orbits} is the present-day location of the LMC (open black circle), the present-day location of \clustername\ (filled black circle), the past orbit of the LMC over the same period, and the projected future orbit of the LMC (dashed line), all excluding the \lmcsmc\ as a mass component.
For the two lower LOS velocity cases, the orbit of \clustername\ crosses the midplane of the Galactic disk at a time comparable to the age of the cluster (i.e. when the color is darkest, corresponding to a time $\approx -130~\textrm{Myr}$).
However, while the orbits of \clustername\ and the LMC are generally in the same orbital plane and have the same sense about the Galaxy, none of the orbits closely approach (within the half-mass radius of our Hernquist model for the LMC) or cross the orbit of the LMC (even when including the LMC mass component).
This is expected if the gas was shocked or otherwise lost kinetic energy through, e.g., ram pressure --- as is expected to explain the morphology of the LA material \citep[e.g.,][]{Hammer:2015} --- during or before the star formation event that produced \clustername.
We therefore posit that the orbit of \clustername\ can be explained as having originated from the \lmcsmc\ system with some loss of orbital energy during the star formation event.

@@

We thank Doug Finkbeiner (Harvard) for contributing to the \decam\ observations that enabled this work.
